Quantum Hoare Types

### 2019-10-30 paper/paper.tex
Add abstract

\textit{Text of abstract \ldots.}

>>>>

\begin{abstract}
	Quantum Computing is a new and upcoming way to utilize Quantum Mechanics to do computation. It is easy to introduce bugs while programming quantum computers similar to classical computing. Strong static type systems have prevented a lot of bugs from being introduced in the classical paradigm. There is a similar need for well-designed types in the domain of quantum computing. We introduce Quantum Hoare Types that let programmers reason statically about certain semantic properties of their quantum programs and further allow limited form of formal verification.
